Echoes from the scattering of wavepackets on wormholes

### 2019-01-15 paper.tex
Add files via upload

\begin{eqnarray}
h_+(x,t)=\frac{C_{\theta}}{r(|x|)}\Psi^{\mathrm{even}}_{20}(x,t),\nonumber\\
h_{\times}(x,t)=\frac{C_{\theta}}{r(|x|)}\Psi^{\mathrm{odd}}_{20}(x,t),\label{eq:pols}
\end{eqnarray}
where $C_{\theta}$ is a constant coming from the normalized spherical harmonics evaluated at $\theta=\pi/2$. Therefore, the existence of echoes might generate a wave with even $(h_+)$ polarization in certain intervals, and with odd $(h_{\times})$ polarization in what remains of the observation time after the transient, as we notice in in Fig.~\ref{fig:pol}. It is interesting to notice these effects are present in the echoes solutions for a spherically symmetric system, even when the excess of power is small. Spin-orbit coupling between the spin and the angular momentum in Kerr-like solutions might enhance the polarization effects.

>>>>

\begin{eqnarray}
h_+(x,t)=\frac{C_{\theta}}{r(|x|)}\Psi^{\mathrm{even}}_{20}(x,t),\nonumber\\
h_{\times}(x,t)=\frac{C_{\theta}}{r(|x|)}\Psi^{\mathrm{odd}}_{20}(x,t),\label{eq:pols}
\end{eqnarray}
where $C_{\theta}$ is a constant coming from the normalized spherical harmonics evaluated at $\theta=\pi/2$. Considering $\sigma=0.6495 r_g$, the parameters of the cavity used in sections \ref{sec:scalar} and \ref{sec:tensor} and the same initial Gaussian pulses for $\Psi^{\mathrm{even}}_{20}(x,t)$ and $\Psi^{\mathrm{odd}}_{20}(x,t)$; we show that the existence of echoes generates an outgoing wave with even $(h_+)$ polarization in certain intervals and with odd $(h_{\times})$ polarization in what remains of the observation time after the transient, as we notice in Fig.~\ref{fig:pol}. It is interesting to notice these effects are present in the echoes solutions for a spherically symmetric system, even when the excess of power is small. Spin-orbit coupling between the spin and the angular momentum in Kerr-like solutions might enhance the polarization effects.
